Turbulence in compact to giant HII regions

### 2022-08-19 strucfunc_paper.tex
Work last week on the correlations

\subsection{Scaling relations between physical properties and turbulent parameters}\label{sec:scaling-relations}

@@

\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}

@@

In the Fig.~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion plane.
The relationship we obtain is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\).
\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work) with a linear relation of \(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \).

>>>>

\subsection{Scaling relations for turbulence parameters}\label{sec:scaling-relations}

@@

\subsubsection{Plane-of-sky vs line-of-sight
  velocity dispersions}
\label{sec:sigmapos-vs-sigmalos}

In the Figure~\ref{fig:los-vs-pos} we show the
mean non-thermal line-of-sight velocity dispersion
\(\langle\sigma\los\rangle\)
(obtained from the spectral line profiles)
versus the plane-of-sky dispersion of mean velocities
\(\sigma\pos\)
(obtained from our structure function fits).
The relationship we obtain is
\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
which can be compared with previous results
using different types of samples.

\citet{2011MNRAS.413..705L} surveyed
a sample of small-to-intermediate size \hii{} regions in M33,
finding
\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
for their sub-sample with higher resolution observations
(21 sources).
This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
which can be seen to be almost identical to our own result. 
Both fits are consistent with a slope of unity and an offset of
\(\SI{8}{km.s^{-1}}\).

\citet{arthur2016turbulence} calculate the relationship
between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
which is shown by the MISSING line in Figure~\ref{fig:los-vs-pos}.
Although this line is a fair representation of the low-\(\sigma\)
points in our sample, it fails badly for highest dispersion source,
30~Doradus.

A clear outlier from the general trend

@@

At least three different
